Using traffic analysis to identify The Second Generation Onion Router

### 2011-01-30 thesis/thesis.tex
Put results in table section, confident methodology, put 3 in parencite postnote, rather than 'page 3'

Tor is one of the most successful and widely deployed anonymous networks, with
around one thousand, eight hundred users at the time of writing
\parencite{website:tor-anonymity-online}. While it has been the subject of many
traffic analysis attacks, the primary objective has historically been the
attempt to reveal participant identities: ``The principal objective of an
adversary attacking an anonymous communication system is to link the initiators
of connections with their respective communication partners and vice versa''
\parencite[page 3]{Murdoch:2005p325}.

@@

The experiment will be conducted in two phases, the first being a data
collection phase. The second phase will include a quasi experimental
methodology which may include data manipulation techniques to prepare the
collected data and a comparison of various heuristics and machine learning
based traffic analysis to classify the collected data.

@@

\begin{tabular}{lrrr}
  \toprule
  & True Positive Rate & False Positive Rate & ROC \\
  \midrule
  Random Forest\\
  \midrule
  HTTPS & 0.957 & 0.036\\
  HTTP over Tor & 0.937 & 0.037\\
  HTTPS over Tor & 0.977 & 0.003\\
  \midrule
  j4.8 With 10 fold cross validation\\
  \midrule
  HTTPS & 0.951 & 0.04\\
  HTTP over Tor & 0.978 & 0.043\\
  HTTPS over Tor & 0.97 & 0.007\\
  \midrule
  Random Tree\\
  \midrule
  HTTPS & 0.961 & 0.046\\
  HTTP over Tor & 0.906 & 0.04\\
  HTTPS over Tor & 0.955 & 0.01\\
  \midrule
  Adaboost\\
  \midrule
  HTTPS & 0.95 & 0.001\\
  HTTP over Tor & 0.999 & 0.324\\
  HTTPS over Tor & 0 & 0\\
  \bottomrule
  \label{table:results}
\end{tabular}

>>>>

Tor is one of the most successful and widely deployed anonymous networks, with
around one thousand, eight hundred users at the time of writing
\parencite{website:tor-anonymity-online}. While it has been the subject of many
traffic analysis attacks, the primary objective has historically been the
attempt to reveal participant identities: ``The principal objective of an
adversary attacking an anonymous communication system is to link the initiators
of connections with their respective communication partners and vice versa''
\parencite[3]{Murdoch:2005p325}.

@@

The experiment will be conducted in two phases, the first being a data
collection phase. The second phase will include a quasi experimental
methodology which will include data manipulation techniques to prepare the
collected data and a comparison of various heuristics and machine learning
based traffic analysis to classify the collected data.

@@

\begin{table}
  \begin{tabular}{lrrr}
    \toprule
    & True Positive Rate & False Positive Rate & ROC \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036\\
    HTTP over Tor & 0.937 & 0.037\\
    HTTPS over Tor & 0.977 & 0.003\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04\\
    HTTP over Tor & 0.978 & 0.043\\
    HTTPS over Tor & 0.97 & 0.007\\
    \midrule
    Random Tree\\
    \midrule
    HTTPS & 0.961 & 0.046\\
    HTTP over Tor & 0.906 & 0.04\\
    HTTPS over Tor & 0.955 & 0.01\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001\\
    HTTP over Tor & 0.999 & 0.324\\
    HTTPS over Tor & 0 & 0\\
    \bottomrule
    \label{table:results}
  \end{tabular}
  \caption{Results}
\end{table}
